Gravitational field calculation in spherical coordinates using variable densities in depth

### 2019-03-08 manuscript/manuscript.tex
Replace "normalize" for "normalize"

The main challenge of the GLQ integration is the loss of accuracy that occurs when the
computation point approaches the tesseroid \citep{Ku1977}.
\citet{Uieda2016} built on the three dimensional adaptive discretization algorithm of
\citet{Li2011} to automatically obtain integration results with 0.1\% accuracy.
The algorithm recursively divides the tesseroid into smaller ones when a
threshold is exceeded,
namely when the normalized distance to the computation point is greater than a
``distance-size ratio'' parameter ($D$).
\citet{Uieda2016} have also obtained standard values of $D$
for the gravitational potential, its gradient and Marussi tensor components
by comparing the numerical integration results with the fields generated by a spherical
shell.

@@

We have developed a complementary discretization algorithm in the redial direction that
takes into account the variations of the density function.
This density-based discretization is applied prior to the two dimensional adaptive
discretization described in the previous section.
In short, the algorithm divides the tesseroid along the radial dimension at the
depths at which the \emph{maximum density variations} take place.

@@

\textit{Step 2}:
Evaluate the normalized density function and straight line on a range of $N$ radii
between $r_1$ and $r_2$.
We have opted for $N = 101$ but the specific value of $N$ is not critical to the
algorithm.

>>>>

The main challenge of the GLQ integration is the loss of accuracy that occurs when the
computation point approaches the tesseroid \citep{Ku1977}.
\citet{Uieda2016} built on the three dimensional adaptive discretization algorithm of
\citet{Li2011} to automatically obtain integration results with 0.1\% accuracy.
The algorithm recursively divides the tesseroid into smaller ones when a
threshold is exceeded,
namely when the normalised distance to the computation point is greater than a
``distance-size ratio'' parameter ($D$).
\citet{Uieda2016} have also obtained standard values of $D$
for the gravitational potential, its gradient and Marussi tensor components
by comparing the numerical integration results with the fields generated by a spherical
shell.

@@

We have developed a complementary discretization algorithm in the radial direction that
takes into account the variations of the density function.
This density-based discretization is applied prior to the two dimensional adaptive
discretization described in the previous section.
In short, the algorithm divides the tesseroid along the radial dimension at the
depths at which the \emph{maximum density variations} take place.

@@

\textit{Step 2}:
Evaluate the normalised density function and straight line on a range of $N$ radii
between $r_1$ and $r_2$.
We have opted for $N = 101$ but the specific value of $N$ is not critical to the
algorithm.
